Pillar 1 - Sequential Pattern Mining

### 2019-03-12 Pillar 1 - Sequential Pattern Mining.Rmd
Create d_transcript_augmented in set up section for simplicity
Simplify code for d_transactions$G
Use cumany() instead of spread - gather

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(d_course, by = c("Course ID"))

@@

  # Spread along ceiling grades
  mutate(
    grade_ceil = ceiling(Grade),
    Values     = TRUE,
    id         = 1 : n() # to ensure each row is unique
    ) %>%
  spread(
    key   = grade_ceil, 
    value = Values
    ) %>%

  # grade x or lower
  mutate(
    `1`  = `0`|`1`,
    `2`  = `1`|`2`,
    `3`  = `2`|`3`,
    `4`  = `3`|`4`,
    `5`  = `4`|`5`,
    `6`  = `5`|`6`,
    `7`  = `6`|`7`,
    `8`  = `7`|`8`,
    `9`  = `8`|`9`,
    `10` = `9`|`10`
    ) %>%

  # Gather along rounded grades
  gather(
    key   = grade_ceil,
    value = X,
    `0` :`10`, 
    na.rm   = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    ) %>%

  # Identifying item
  mutate(
    item_G = paste(item, grade_ceil, sep = "_")
    )
```
####Save d_transactions
```{r save d_transaction}
save(
  d_transactions,
  file = "Output/transaction_df.RDATA"
  )
```
### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE, warning = FALSE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%

>>>>

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(select(d_course, - Period), by = c("Course ID"))

@@

  mutate(row_of_origin = TRUE) %>%

  complete(
    nesting(sequenceID, eventID, item, Grade), grade_ceil,
    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
    ) %>%

  group_by(sequenceID, eventID, item, Grade) %>%

  distinct(sequenceID, eventID, item, grade_ceil, Grade, row_of_origin) %>% # reminder that we should get rid of duplicates oin d_transcript

  arrange(grade_ceil) %>%

  filter(cumany(row_of_origin)) %>% # only keep grades larger than ceil_grade

  ungroup()
```
####Save d_transactions
```{r save d_transaction}
save(
  d_transactions,
  file = "Output/transaction_df.RDATA"
  )
```
### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE, warning = FALSE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%
